### 2017-06-21 manuscript/usses_water_ms.Rmd
updates stats in ms

\begin{align}
\mu_{i(j(k))} &= \beta_{0,j(k)} + \beta_{1,j(k)}x_i, \\
y_{i(j(k))} &\sim \text{Normal} \left(\mu_{i(j(k))}, \sigma^2_{k} \right),
\end{align}

\noindent{} where $\mu_{i(j(k))}$ is the deterministic prediction from the regression model for observation *i* for plot *j* associated with treatment *k*, $\beta_{0,j(k)}$ is the intercept for plot *j* associated with treatment *k*, $\beta_{1,j(k)}$ is the slope term for the effect of precipitation for plot *j* associated with treatment *k*, and $\sigma^2_k$ is the process variance for treatment *k*.
Data include the standardized log(ANPP) observations ($y_{i(j(k))}$) and precipitation ($x_i$).
Although we include observation subscript *i* on the *x*s, observations within a year all share the same precipitation values.

@@

Unfortunately, we cannot detect whether treatments grow stronger over time in the ANPP-Precipitation model described above because year and precipitation are perfectly colinear.
Therefore, we fit simpler model with log(ANPP) as the response and treatment effects for drought and irrigation (hereafter, 'ANPP-Treatment' model). 
We again use a hierarchical structure, where the treatment effects were allowed to vary by year (i.e., year random effects).
This allowed us to test whether treatment effects got stronger over time.
We also included a plot random effect to account for non-independence of observations through time in a plot.
This model is also fully described in Appendix 2.

We fit both models using a Bayesian approach, obtaining posterior estimates of all unkowns via the No-U-Turn Hamiltonian Monte Carlo sampler in Stan [@stan2016].
We used the R package 'rstan' [@rstan2016] to link R [@R2016] to Stan.
We obtained samples from the posterior distribution for all model parameters from four parallel MCMC chains run for 10,000 iterations, saving every $10^{\text{th}}$ sample.
Traceplots of all parameters were visually inspected to ensure well-mixed chains and convergence.
We also made sure all scale reduction factors ($\hat{R}$) were less than 1.1.

@@

Growing season precipitation had a positive effect on ANPP (mean of $\beta_{1}$ = 0.67; 80\% BCI = 0.24, 1.10; 95\% BCI = -0.11, 1.34) (Fig. 1D).
Average ANPP was similar among treatments (similar intercepts, Fig. 2A), as was the effect of precipitation (similar slopes, Fig. 2B).
In an average precipitation year (i.e., $x$ = 0 in Eq. 1), the probability that ANPP in a drought plot is less than ANPP in a control plot was 0.58, and the probability that ANPP in an irrigation plot is higher than in a control plot was 0.57.
In other words, the posterior distributions of $\beta_0(\text{control}) - \beta_0(\text{drought})$ and $\beta_0(\text{control}) - \beta_0(\text{drought})$ broadly overlapped zero.
There was also no evidence that the treatment effects became more important over time because there was no directional trend in the yearly treatment effects estimated from the ANPP-Treatment model (Fig. 3).

Community composition was similar among treatments, whether looking at basal cover or density (Fig. 4).
Likewise, community composition was remarkably stable over time, with no evidence of divergence among treatments (Fig. 4).
Species' abundances and ranks showed little deviation over the five-year experiment, regardless of treatment (Fig. 5).

>>>>

\begin{align}
\mu_{i(j(k(t)))} &= \beta_{0,j(k)} + \beta_{1,j(k)}x_i + \gamma_t, \\
y_{i(j(k(t)))} &\sim \text{Normal} \left(\mu_{i(j(k(t)))}, \sigma^2_{k} \right),
\end{align}

\noindent{} where $\mu_{i(j(k))}$ is the deterministic prediction from the regression model for observation *i* for plot *j* associated with treatment *k* in year *t*, $\beta_{0,j(k)}$ is the intercept for plot *j* associated with treatment *k*, $\beta_{1,j(k)}$ is the slope term for the effect of precipitation for plot *j* associated with treatment *k*, $\gamma_t$ is the intercept offset for year *t*, and $\sigma^2_k$ is the process variance for treatment *k*.
Data include the standardized log(ANPP) observations ($y_{i(j(k(t)))}$) and precipitation ($x_i$).
Although we include observation subscript *i* on the *x*s, observations within a year all share the same precipitation values.

@@

<!---
Unfortunately, we cannot detect whether treatments grow stronger over time in the ANPP-Precipitation model described above because year and precipitation are perfectly colinear.
Therefore, we fit simpler model with log(ANPP) as the response and treatment effects for drought and irrigation (hereafter, 'ANPP-Treatment' model). 
We again use a hierarchical structure, where the treatment effects were allowed to vary by year (i.e., year random effects).
This allowed us to test whether treatment effects got stronger over time.
We also included a plot random effect to account for non-independence of observations through time in a plot.
This model is also fully described in Appendix 2.
---->

We fit the model using a Bayesian approach, obtaining posterior estimates of all unkowns via the No-U-Turn Hamiltonian Monte Carlo sampler in Stan [@stan2016].
We used the R package 'rstan' [@rstan2016] to link R [@R2016] to Stan.
We obtained samples from the posterior distribution for all model parameters from four parallel MCMC chains run for 10,000 iterations, saving every $10^{\text{th}}$ sample.
Traceplots of all parameters were visually inspected to ensure well-mixed chains and convergence.
We also made sure all scale reduction factors ($\hat{R}$) were less than 1.1.

@@

Cumulative growing season soil moisture had a positive effect on ANPP (mean of $\beta_{1}$ = 0.43; 80\% BCI = -0.05, 0.88; 95\% BCI = -0.36, 1.15) (Fig. 1D).
Average ANPP was similar among treatments (similar intercepts, Fig. 2A), as was the effect of precipitation (similar slopes, Fig. 2B).
In an average precipitation year (i.e., $x$ = 0 in Eq. 1), the probability that ANPP in a conrol plot is greater than ANPP in a drought plot was 0.71, and the probability that ANPP in a control plot is lower than in an irrigation plot was 0.41.
In other words, the posterior distributions of $\beta_0(\text{control}) - \beta_0(\text{drought})$ and $\beta_0(\text{control}) - \beta_0(\text{drought})$ broadly overlapped zero.
There was also no evidence that the treatment effects became more important over time because there was no directional trend in the yearly treatment effects estimated from the ANPP-Treatment model (Fig. 3).

Community composition was similar among treatments.
In no year did community composition among treatments not overlap, and they were equally dispersed in all years (Fig. 4).
Likewise, community composition was remarkably stable over time, with no evidence of divergence among treatments (Fig. 4).
Species' abundances and ranks showed little deviation over the five-year experiment, regardless of treatment (Fig. 5).
